### 2013-04-03 R/reportmd.Rmd
Metadata information include; metadata files standardised

### Method - please provide any missing information/follow template
```{r echo=FALSE, message=FALSE, warning=FALSE, comment=''}
printMeta(.dat$data)
```

>>>>

### Method - please provide any missing information/follow template
```{r echo=FALSE, message=FALSE, warning=FALSE, comment=''}
metaTable  <-  printMeta(.dat$data)
for(j in 1:nrow(metaTable)){
  cat(paste0(metaTable[j,1], ": ", metaTable[j,2], "\n"))
}

```
